### 2023-01-03 paper.Rmd
added APA7 support

documentclass     : "apa6"
output            : 
  papaja::apa6_pdf
appendix: "appendix.Rmd"

header-includes:
  - \usepackage{setspace}
---

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

>>>>

output            : 
  papaja::apa6_pdf
appendix: "appendix.Rmd"

header-includes:
  - \usepackage{setspace}
  - \usepackage{float}
  - \floatstyle{plaintop}
  - \restylefloat{figure}
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
---

@@

\begingroup
<div id="refs" custom-style="Bibliography"></div>
\endgroup
